Develop atlantisom wrappers

### 2020-01-17 WrapperDevelopment.Rmd
current wrapper and SS3dat output

Use the saved outputs of above to write a Stock Synthesis dat file

@@

require(r4ss)
#still needs omlist_ss and all this stuff
source(here("/config/CC3Config_sardLWcorr.R"))
source(here("/config/omdimensions.R"))
source(here("/config/sardinesurvey.R"))
source(here("/config/sardinefishery.R"))

@@

@@

@@

stocksynthesis.data$CPUE

@@

>>>>

Use the saved outputs of above to write a Stock Synthesis dat file
This is not a function yet, copy in Christine's

@@

require(r4ss)
omlist_ss<-CC3om_sardine
source(here("/config/CC3Config_sardLWcorr.R"))
source(here("/config/omdimensions.R"))
source(here("/config/sardinesurvey.R"))
source(here("/config/sardinefishery.R"))

@@

#Years to survey, assuming survey is once per year
#survey_years <- survey_sample_full[(burnin+1):(burnin+nyears)] # my original
survey_years <- survey_sample_full[burnin:(burnin+nyears-1)] #from Christine's new sardine_config.R

@@

survObsBiom <- survObsBiom[[1]]
truecatchbio_ss <- truecatchbio_ss[[1]]

#add this to om_indices function so that this has years when read in
truecatchbio_ss$time <- as.integer(truecatchbio_ss$time/365)

@@

#test  
stocksynthesis.data$CPUE

@@

#read in comp data
age_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "survObsAgeComp.rds")))
age_comp_data <- age_comp_data[[1]]

fish_age_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsAgeComp.rds")))
fish_age_comp <- fish_age_comp[[1]]

#Get the age bins
age_bin_names <- names(stocksynthesis.data$agecomp)[10:length(names(stocksynthesis.data$agecomp))]
age_bins <- sub("a","",age_bin_names)

require(maditr)
# add dependency on maditr::dcast to atlantisom
age_comp_flat <- atlantisom::reformat_compositions(age_comp_data,
                     round.places = 4,
                     comp_type = "agecomp")

## Write age composition data for survey
stocksynthesis.data <- atlantisom::SS_write_comps(ss_data_list = stocksynthesis.data,
               comp_matrix = list(age_comp_flat[burnin:(burnin+nyears-1),]),
               data_rows = list(stocksynthesis.data$styr:(stocksynthesis.data$styr+nyears-1)),
               sampling_month = list(rep(survey_month,nyears)),
               data_type = c("agecomp"),
               fleet_number = c(1),
               bins = list(age_bins),
               caal_bool = c(FALSE))
stocksynthesis.data$agecomp

#length comps
len_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "survObsLenComp.rds")))
fish_len_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsLenComp.rds")))

len_comp_data <- len_comp_data[[1]]
fish_len_comp_data <- fish_len_comp_data[[1]]

if(fstepperyr>1){
  fish_len_comp_anndata <- fish_len_comp_data %>%
    mutate(yr = floor(time/fstepperyr)) %>%
    group_by(species, agecl, lower.bins, upper.bins, time=as.integer(yr)) %>%
    summarise(annnatlength=sum(atoutput)) %>%
    rename(atoutput = annnatlength)
} else {
  fish_len_comp_anndata <- fish_len_comp_data
}

caal_comp_flat <- atlantisom::reformat_compositions(len_comp_data,                                round.places=4,
                comp_type="caalcomp")

#remove burnin
caal_comp_final <- filter(caal_comp_flat,
                         time %in% survey_years)

#Add over age classes to get sample size
len_comp_flat <- atlantisom::reformat_compositions(len_comp_data,
                                  round.places = 0,
                           comp_type="lencomp")
#remove burnin
len_comp_final <- filter(len_comp_flat,
                         time %in% survey_years)

length_bins <- as.integer(names(len_comp_final))
length_bins <- length_bins[!is.na(length_bins)]

# fishery length comps are still 5 timesteps per year
# need to aggregate to annual (done above)
# also,  make effN annual goal/fstepsperyr (done above)
fish_len_comp_flat <- atlantisom::reformat_compositions(fish_len_comp_anndata,
                                  round.places = 0,
                           comp_type="lencomp")

#remove burnin works after adjustment above
fish_len_comp_final <- filter(fish_len_comp_flat,
                         time %in% fish_years)

notbins <- c("time", "nsamp")

# fish_length_bins <- as.integer(names(fish_len_comp_final))
# fish_length_bins <- fish_length_bins[!is.na(fish_length_bins)]

# need to fill empty length bins with 0s to have same bins as survey for SS_write_comps
missing.lengths <- setdiff(length_bins, names(fish_len_comp_final)[!names(fish_len_comp_final) %in% notbins])
fish_len_comp_final[as.character(missing.lengths)] <- 0                    # Add them, filled with '0's
fish_len_comp_final <- fish_len_comp_final[c("time", length_bins, "nsamp")]

# fishery age comps also 5 timesteps per year
if(fstepperyr>1){
  fish_age_comp_anndata <- fish_age_comp %>%
    mutate(yr = floor(time/fstepperyr)) %>%
    group_by(species, agecl, time=as.integer(yr)) %>%
    summarise(annnatage=sum(atoutput)) %>%
    rename(atoutput = annnatage)
} else {
  fish_age_comp_anndata <- fish_age_comp
}

fish_age_comp_flat <- atlantisom::reformat_compositions(fish_age_comp_anndata,
                           comp_type="agecomp")

#remove burnin (not necessary?fish comps made with fish_years only) 
fish_age_comp_final <- filter(fish_age_comp_flat,
                         time %in% fish_years)

# #SS_write_comps breaking because fishery age bins start with 2 not 1; extracting bins from fish file may help?
# fish_age_bins <- names(fish_age_comp_flat)[!names(fish_age_comp_flat) %in% notbins]

# that leaves an empty column in data file, so instead fill with 0s
missing.ages <- setdiff(age_bins, names(fish_age_comp_final)[!names(fish_age_comp_final) %in% notbins])
fish_age_comp_final[missing.ages] <- 0                    # Add them, filled with '0's
fish_age_comp_final <- fish_age_comp_final[c("time", age_bins, "nsamp")]

comp_list <- list(caal_comp_final,len_comp_final, fish_age_comp_final, fish_len_comp_final)

apply_month <- list(rep(survey_month, nrow(comp_list[[1]])), 
                    rep(survey_month, nrow(comp_list[[2]])),
                    rep(fishing_month,nrow(comp_list[[3]])),
                    rep(fishing_month,nrow(comp_list[[4]])))

# This now runs by ensuring that survey and fishery compositions have the same bins 
# (filled with 0s for missing bins in fishery relative to survey)

# Write CAAL and length composition data
stocksynthesis.data <- atlantisom::SS_write_comps(ss_data_list = stocksynthesis.data, 
                                      comp_matrix = comp_list, 
                                      data_rows = list((comp_list[[1]]$time-survey_sample_time)/timestep + 1 , (survey_years-survey_sample_time)/timestep + 1,fish_years,fish_years),
                                      sampling_month = apply_month, 
                                      data_type = rep(c("agecomp", "lencomp"),2), 
                                      fleet_number = c(2,2,1,1),  
                                      bins = list(age_bins, 
                                                  length_bins, 
                                                  age_bins, 
                                                  length_bins), 
                                      caal_bool = c(TRUE, rep(FALSE,3)))

head(stocksynthesis.data$lencomp)
head(stocksynthesis.data$agecomp)

#Change length bin structure to match atlantis data
stocksynthesis.data$lbin_vector <- length_bins

#Get correct number of length bins
stocksynthesis.data$N_lbins <- length(length_bins)

#Set lbin_method to 1 - this makes the population length bins match the data bins 
#When lbin_method==1, we just comment out the binwidth, minimum, and maximum size arguments since they aren't used
stocksynthesis.data$lbin_method <- 1
stocksynthesis.data$binwidth <- "#"
stocksynthesis.data$minimum_size <- "#"
stocksynthesis.data$maximum_size <- "#"

#Change minimum sample size to 0.001 for CAAL data (SS won't let it go lower than this)
stocksynthesis.data$age_info$minsamplesize <- rep(0.001,2)

SS_writedat_3.30(stocksynthesis.data, outfile = paste0("./inst/extdata/",model_dir,
datfile_name),
                 overwrite=TRUE)
